Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement

### 2020-12-28 vesicle_code/docs/permeableVes/main.tex
fixed up figure 5

Our simulations indicate the semi-permeability does affect the excess
pressure, and the vesicle's reduced area reduces by about 6.1\%
(Figure~\ref{fig:stenosisComposite}(d)). Since the area does decrease at
a constant rate we expect that a larger amounts of deflation is possible
if the vesicle is stenosed for a longer period of time. Therefore, in
Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
through a channel of double the length, and we observe that the reduced
area decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).
\todo[inline]{This example also used a smaller flow rate of $8.4\mu$m/s}

\begin{figure*}[htp]
  \ifTikz
  \input{figures/stenosisComposite.tikz}
  \else
  \includegraphics{figures/stenosisComposite.pdf}
  \fi
  \caption{\label{fig:stenosisComposite} (a) A semi-permeable vesicle
  passing through a constricted geometry similar to the experimental
  device in~\cite{abk-fai-sto2006}. (b) A semi-permeable vesicle passing
  through a constricted geometry that is over five times longer. (c) The
  excess pressure of an impermeable and semi-permeable vesicle in the
  short geometry in (a). (d) The reduced area of the semi-permeable
  vesicle in the short geometry in (a). (e) The reduced area of the
  semi-permeable vesicle in the long geometry in (b). In parts (c), (d),
  and (e), the horizontal axis is the x-coordinate of the vesicle's
  center of mass.}
\end{figure*}

>>>>

Our simulations indicate the semi-permeability does affect the excess
pressure, and the vesicle's reduced area reduces by about 6.1\%
(Figure~\ref{fig:stenosisComposite}(d)). Since the area does decrease at
a constant rate we expect that a larger amounts of deflation is possible
if the vesicle is stenosed for a longer period of time. Therefore, in
Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
through a channel of triple the length, and we observe that the reduced
area decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).
\begin{itemize}
  \item In plot (a), flow rate is $1000 \mu m/s$ and residency time is
    $t_R = 45.6 \times 10^{-2}$ s.
  \item In plot (b), flow rate is $8.4 \mu m/s$ and residency time is
    $t_R =  16.2$ s.
\end{itemize}

\begin{figure*}[htp]
  \ifTikz
  \input{figures/stenosisComposite.tikz}
  \else
  \includegraphics{figures/stenosisComposite.pdf}
  \fi
  \caption{\label{fig:stenosisComposite} (a) A semi-permeable vesicle
  passing through a constricted geometry similar to the experimental
  device in~\cite{abk-fai-sto2006}. (b) A semi-permeable vesicle passing
  through a constricted geometry that is over five times longer. (c) The
  excess pressure of an impermeable and semi-permeable vesicle in the
  short geometry in (a). (d) The reduced area of the semi-permeable
  vesicles in the geometries in (a) and (b) as a function of the
  vesicles' center of mass. The $x$-axis is scaled by $1/L$ where $L$ is
  half the length of the constriction. (e) The reduced area of the
  semi-permeable vesicles in the geometries in (a) and (b) as a function
  of time. The time axis is scaled by $1/t_R$ where $t_R$ is the
  residency time. In parts (c) and (d), the dashed lines correspond to
  the locations of the inlet and outlet. In part (e), the dashed lines
  correspond to the times that the vesicle enters and exits the
  constriction.}
\end{figure*}
